Towards Transparency and Open Science

### 2023-02-19 manuscript.Rmd
spotted one more can not
replace url with zenodo doi

You are reading version ``r repro::current_hash(backend = "gert")``.
This work is made available online under the following source under the terms of the [Creative Commons Universal Public Domain Dedication | CC0](https://creativecommons.org/publicdomain/zero/1.0/):  
<https://aaronpeikert.github.io/thesis/manuscript.pdf>

@@

As a first step, it can be noted that one may split $\mathcal{C}$ in complexity that can be formally described and a part that can only be evaluated subjectively.
Formal discription, in the strict sense, means that the complexity can be mathematically derived, and in a looser sense, that the process can be repeated at will.
If a researcher employs a linear model, the complexity is calculable parametrically.
Even if it were not calculable, the linear model could be fitted on a large set of other data to assess its expected inductive behavior nonparametrically.
However, suppose the researcher reconsiders the model based on their results and their internal cognitive model (including prior knowledge, expectations, cognitive biases).
For example, based on worse-than-expected results and their intuition, they decided to add a predictor to the model.
In that case, the complexity can not be formally judged because the researcher is an intractable part of the inductive process.
The researcher cannot be asked to repeat the process on all possible data sets, nor is their behavior mathematically well-defined.
However, it is known that the resulting linear model is more complex than a linear regression formally implies.

>>>>

This work (version ``r repro::current_hash(backend = "gert")``) is made available online under the following source under the terms of the [Creative Commons Universal Public Domain Dedication | CC0](https://creativecommons.org/publicdomain/zero/1.0/):  
<https://doi.org/10.5281/zenodo.7654989>

@@

As a first step, it can be noted that one may split $\mathcal{C}$ in complexity that can be formally described and a part that can only be evaluated subjectively.
Formal discription, in the strict sense, means that the complexity can be mathematically derived, and in a looser sense, that the process can be repeated at will.
If a researcher employs a linear model, the complexity is calculable parametrically.
Even if it were not calculable, the linear model could be fitted on a large set of other data to assess its expected inductive behavior nonparametrically.
However, suppose the researcher reconsiders the model based on their results and their internal cognitive model (including prior knowledge, expectations, cognitive biases).
For example, based on worse-than-expected results and their intuition, they decided to add a predictor to the model.
In that case, the complexity cannot be formally judged because the researcher is an intractable part of the inductive process.
The researcher cannot be asked to repeat the process on all possible data sets, nor is their behavior mathematically well-defined.
However, it is known that the resulting linear model is more complex than a linear regression formally implies.
